### 2016-03-09 paper/algorithm.tex
yasu

\section{Swarm Fusion Method}
\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
parallel extension of Fusion Move Method. Take a multi-threading
environment to explain our idea, which is also applicable to other
parallel computation environments such as cloud computing. Assume we
have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
collect solutions or solution proposals for fusion. First, the {\it
proposal pool} can generate new solution proposals on request.
%
Second, the {\it solution pool} stores the solutions that have been
fused by the threads. At default, each thread keeps only a current
solution in the pool, but the scheme can be more general. Two
parameters $\alpha_i$ and $\beta_i$ control the behavior of each fusion
step in $T_i$. The thread collects $\alpha_i$ solution proposals
from the proposal pool and $\beta_i$ solutions from the solution pool
for fusion in each step.
%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

@@

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/base_illustration.png}
 \caption{Base Swarm Fusion architecture.}\label{fig:base}
\end{figure}

>>>>

\section{Swarm Fusion Method}
\yasu{need to polish, reads very bad.}  {\it Swarm Fusion} (SF) is a
natural parallel extension of Fusion Move method (FM). Take a
multi-threading environment to explain our idea, but the technique is also
applicable to other parallel programming model such as {\it MapReduce}
in cloud computing.
%
Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion, while FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. We have 1) a {\it proposal pool}, from which we pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we pick arbitrary number of
intermediate solutions generated by all the threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

Two parameters $\alpha_i$ and $\beta_i$
control the behavior of each fusion step in $T_i$. The thread collects
$\alpha_i$ solution proposals from the proposal pool and $\beta_i$
solutions from the solution pool for fusion in each step.
%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

Five architectures.

Sequential.
Naive parallel sequential (viktor).
H-fusion (veksler, delong)
Ours (sharing solutions)
Ours (multiple proposals)
Ours (multiple proposals and sharing solutions)

@@

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf}
 \caption{Base Swarm Fusion architecture.}\label{fig:base}
\end{figure}

% \begin{figure}[tb]
%  \includegraphics[width=\columnwidth]{figure/model2.pdf}
%  \caption{Base Swarm Fusion architecture.}\label{fig:base}
% \end{figure}
